---
title: "The basic R Markdown"
author: "Dean Rossano"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Data Description


The dataset consists of the following information collected from 397 collegiate professors in the US from 2008 to 2009:


* Rank: Professor's rank of either assistant professor, associate professor, or professor.
* Discipline: The department that the professor works in, either applied or theoretical
* yrs.since.phd: Number of years sisnce the professor has obtained their PhD
* yrs.service:Number of year the professor has served the department and/or university
* sex: Professors sex of either male or female
* salary: Professor's nine-month salary (USD)
# Data Wrangling
```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
