---
title: "The basic R Markdown"
author: "Dean Rossano"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Data Description


The dataset consists of the following information collected from 397 collegiate professors in the US from 2008 to 2009:


* Variable 1: Rank - Professor's rank of either assistant professor, associate professor, or professor
* Variable 2: Discipline - The department that the professor works in, either applied or theoretical
* Variable 3: yrs.since.phd - Number of years sisnce the professor has obtained their PhD
* Variable 4: yrs.service - Number of year the professor has served the department and/or university
* Variable 5: sex - Professors sex of either male or female
* Variable 6: salary - Professor's nine-month salary (USD)
# Data Wrangling
The following steps and code were used to manipulate the salaries dataset:
* Step 1: Load the tidyverse package
* Step 2: Set the working directory to the location of Salaries.csv and load Salaries.csv
* Step 3: Use the select function to select the rank, discipline, sex, & salary columns
* Step 4: Use the filter function to filter out the rows where salary is not a missing value
* Step 5: Use group_by to group the data based on rank, discipline, and sex and then use count to tally the amount of rows
* Step 6: Use mutate and spread to reshape the table from long to wide based on the sex column
* step 7: Use gather to reshape the table back to a long shape.
```{r echo=TRUE, message=FALSE}
# Add your code here for this assignment. 

# load tidyverse package
library(tidyverse)

# set the working directory to Module 2 & load the Salaries.csv dataset
setwd("Module3")
salaries = read_csv("Salaries.csv")

# select the columns of rank, discipline, sex and salary
salaries %>% 
  select(rank, discipline, sex, salary)

# filter the rows where salary is not a missing value
salaries %>%   
  filter(!is.na(salary))

# group based on rank, discipline and sex and tally count of rows
salaries %>% 
  group_by(rank, discipline, sex) %>% 
  count(rank, discipline, sex)

# reshape table from long to wide based on sex column
wide <- salaries %>% 
  # remove duplicate entries
  unique() %>% 
  mutate(sex_logical=TRUE) %>% 
  spread(sex, sex_logical,fill = FALSE)

# reshape the table from wide to long
long <- wide %>% 
  gather(sex,logical_value, (ncol(wide)-1):ncol(wide),na.rm = TRUE) %>% 
  mutate(logical_value = NULL)
```
